---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# plotDK

plotDK provides easy access to plot summary statistics as choropleth maps of danish administrative areas. plotDK supports 
geoms for danish regions, provices, municipalities, and zipcodes. 

## Installation

You can install the released version of plotDK from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("plotDK")
```

or from github with:

``` r
devtools::install_github("https://github.com/kristianSN/plotDK")
```

## Empty maps

To simply show a choropleth map of a chosen administrative level (here regions) invoke:

```{r example-empty-regions, message = FALSE}
library(plotDK)

plotDK(plotlevel = "region")

```

Switching to plot municipalities is as simply as switching the plotlevel to "municipality":

```{r example-empty-municipalities, message = FALSE}

plotDK(plotlevel = "municipality")

```


## Plotting summary statistics on municipalities

To fill the maps with values, first generate or load a data set containing one row per entity, with a valid ID column and a value column to be plotted. 
plotDK contains information of valid ID's. For municipalities this data is saved in:

``` r
plotDK::municipality_info
```

Here let's generate a dataset with valid region ID's and assign each region a random numeric value:

```{r example-data-municipalities}
valid_ids <- plotDK::municipality_info

municipality_data <- data.frame(
  municipality_name = valid_ids$municipality_names,
  numeric_value = sample(1:100, size = length(valid_ids$municipality_names), replace = TRUE),
  stringsAsFactors = FALSE
)

municipality_data[1:20,]

```

Plotting these values on their municipalities is as simple as providing the municipality data to plotDK(), while providing the names of the ID and value variables:

```{r example-plot-municipalities, message = FALSE}

plotDK::plotDK(
  data = municipality_data,
  id = "municipality_name",
  value = "numeric_value",
  plotlevel = "municipality"
)

```

The value scales depends upon the type of the value variable. That is means if we try to plot a character or factor variable, the plot will change accordingly:

```{r example-plot-municipalities-factor, message = FALSE}
municipality_data <- data.frame(
  municipality_name = valid_ids$municipality_names,
  factor_value = factor(sample(c("a", "b"), size = length(valid_ids$municipality_names), replace = TRUE)),
  stringsAsFactors = FALSE
)

plotDK::plotDK(
  data = municipality_data,
  id = "municipality_name",
  value = "factor_value",
  plotlevel = "municipality"
)
```


## ggplot compatability

The resulting plots are ggplot2-objects. This means that they can be altered or styled with normal ggplot elements:

```{r example-adding-title-and-switching-legend-label}
library(ggplot2)
p <- plotDK::plotDK(
  data = municipality_data,
  id = "municipality_name",
  value = "factor_value",
  plotlevel = "municipality"
)

p + 
  ggtitle("Some title") +
  scale_fill_manual(
    values=c("firebrick", "darkgoldenrod"),
    name = "Letters"
  ) + 
  theme(
    panel.background = element_rect(
      fill = "lightblue"
    )
  )

```

## Subplots

By default plotDK does not show missing entities. This means that subplots can easily be drawn, by only providing a subset of entities in the data:

```{r subplot}
municipality_data <- data.frame(
  municipality_name = c("frederiksberg", "københavn"),
  factor_value = c("A", "B"),
  stringsAsFactors = FALSE
)

p <- plotDK::plotDK(
  data = municipality_data,
  id = "municipality_name",
  value = "factor_value",
  plotlevel = "municipality"
)

p


```


If you only have data on a subset of entities, but want the entire map drawn, do this by passing the argument; show_missing = TRUE:

```{r subplot_full}

p <- plotDK::plotDK(
  data = municipality_data,
  id = "municipality_name",
  value = "factor_value",
  plotlevel = "municipality",
  show_missing = TRUE
)

p

```


